### 2023-11-03 Scripts/Manuscript/manuscript.Rmd

@@

@@

@@

@@

@@

>>>>

In the current study, measurement error and QMPs were assessed in both replications and original research. These measurement related concepts were then linked to replicability in order to investigate them as potential causes inhibiting successful replications. The results of the tests for the hypotheses showed mixed results. However, when including exploratory and descriptive analyses, a clearer picture of the state of measurement in replication and original research emerges.

Before interpreting of the results, it should be reiterated that the sample size for several analyses was smaller than what is generally recommended for such analyses. This holds especially for the tests of hypotheses 2, & 3, since the number of measures for which reliability could be calculated for these analyses was only eighteen. This was less than anticipated, which brings us to the first topic of the discussion.

@@

This thesis assessed the quality of measurement and measurement reporting in original and replication research by investigating the quality of measurement in the Many Labs projects. Findings were in line with similar investigations in the literature by @shaw2020measurement & @flake2022construct. These two studies found that sufficient validity evidence and reliability reporting for measures was lacking, even more so for replications than for original studies. The lack of support found for hypothesis 1 shows that this also held for this thesis' sample. In fact, support was found for an effect in the direction opposite to what was hypothesized in the preregistration, as the original articles reported reliability coefficients more often than replication studies.

However, even the original articles only reported reliability for approximately one third of the used multiple item measures. Reliability coefficients were reported in such small numbers that the original analysis plan for hypothesis 1 was altered, from evaluating the reliability coefficient value to the number of times reliability was reported in an article or protocol. As a result, the interpretation of rejecting the hypothesis based on this new test changed compared to the preregistered test. Still, the test provides evidence towards the same point, which is that reliability evidence for the used measure is lacking more in replication protocols than in original articles, although most multiple item measures in original articles were also reported without reliability evidence. This shows that lack of reliability evidence is a widespread issue, something that has been shown in earlier literature on this topic [@vacha1999practices; @green2011recent].

Furthermore, across measures used in both original and replication studies, less than half of the measures were multiple item scales. Research commonly made use of single item measures (see Figure XXX for more details), an observation that was also made by @shaw2020measurement. The use of these single item measures comes with risks, since by virtue of being singular they assume that whatever they are measuring is unidimensional, while not being able to test this assumption [@shaw2020measurement]. This is potentially quite worrying given that the exploratory analyses of the multiple item measures, for which unidimensionality could be tested, showed only little support for unidimensionality of the measures used in replications. While the measures that were tested for unidimensionality were mostly used as single indicators in the analyses for the replication protocol, one could argue this does not necessarily mean these measures all assessed constructs with a unidimensional structure. For example, IQ is often used as a singular indicator, even though it consists of several factors [@weiss2013wisc]. However, it should be noted that at least with respect to Many Labs 2, all of the measures that were considered unidimensional for the analyses in this thesis were also considered unidimensional in the investigation by @shaw2020measurement} who also observed a lack of unidimensionality evidence in their investigation of Many Labs 2. To conclude, there is an indication that validity evidence for measures used in replication research is lacking overall.

Several results did show more promising findings for the way measurement related issues are treated in replications. Firstly, the support found for hypothesis 2 showed some evidence that most of the variability in reliability coefficients is between measures, rather than within measures across different locations. If variation in the reliability of a measurement across locations is little, it could indicate that the measurement operated similarly across these locations, which would make the scores from the different lab locations directly comparable and aggregatable. However, again the small sample number of measures for which reliability could be assessed does mean that this estimate remains uncertain. Secondly, most replication protocols clearly stated that their measure was either newly created or based on existing materials. Still, in most instances neither original nor replication provided information on the exact version of their measure. This may largely be due to the fact that many of the used measures were single-item, for which specifying the exact versions may not be seen as crucial because they more or less describe themselves. Finally, QMPs were overall less common in replication protocols than they were in original articles, supporting hypothesis 4. This runs counter to the findings of @shaw2020measurement & @flake2022construct, who found that measures came with less validity evidence in replications than in original studies, as the result of QMPs.

The structured replication protocols that were used in the Many Labs projects, I suspect improved the reporting practices and measurement consistency in replication protocols compared to original articles. Most replication protocols even contained a section under each replicated study, which listed any deviations from the original and as a result many potential QMPs were averted. [@protzko2020high] already demonstrated that transparent reporting of methodology before conducting research can improve the robustness of psychological science, and I believe the same holds true here.

@@

Besides assessing the overall quality of measurement reporting, this thesis also investigated if the reliability of a measure, and QMPs can impact replicability. First of all, contrary to expectations (see Hypothesis 3), less reliable measures were not associated with a decrease in replicability. This result is surprising, since @stanley2014expectations demonstrated the potential impact that measurement error can have on the veracity of determining replication success based on a significance test without attenuating for measurement error. The significance test cut-off criteria that was used in this thesis to assess replication success similarly did not attenuate for measurement error, and thus results in line with the simulation studies of @stanley2014expectations were expected.

While no evidence for hypothesis 3 was found, caution in interpreting the test results is needed. The number of measures for which reliability was calculated was quite low (eighteen for Cronbach's alpha, fifteen for omega), it could be that the test was simply underpowered to detect the effect. On the other hand, it might be that the detrimental influence of measurement error on interpretations of replication results is small in large scale replication projects. Across the multiple replications, measurement error's influence on the effect could have been cancelled out at the meta-analytic level. This would require the measurement error to be random and small, and as a result the average value of the effect and the error around would remain similar, thus not altering the result of the meta-analytic significance test.

Results regarding the relationship between QMPs and replicability were more in line with expectations. In particular, support was found for hypothesis 5, showing that an increase in total QMP ratio was associated with a decrease in replicability. Existing literature has already warned about the potential detrimental effects of QMPs on replications [@shaw2020measurement; @flake2022construct]. This result provides further evidence supporting these claims. However, the association was only significant when data was used from the revised coding protocol, data from the initial protocol, which was more stringent in its assessment of QMP, did not indicate a significant association with replicability.

Similarly, the test for hypothesis 6 showed inconsistent results between the revised and initial coding protocols. Only for the revised protocol data was an increase in total QMPs in the original study associated with an increase in total QMPs in the protocol of the replication for that study. The result obtained with the data from the revised protocol are in line with expectations. If information on measurement is lacking or the measure is poorly motivated in a study, then any subsequent replication attempt will lack information needed match its measurement to the original. Even if it does match the original, when the measure itself is a poor indicator of the assessed variable or construct, both the original and replication data obtained from this measure may not substantially relate to the investigated psychological phenomenon the original study set out to investigate [@flake2022construct]. However, the fact that the conclusions were different based on the protocol makes it difficult to determine the exact nature of the influence of original study QMPs on replication protocol QMPs.

Further analyses based on the QMP ratios of each specific type indicated that across both the initial and revised coding protocols together, only selection, definition, and quantification QMPs in the original article related significantly to selection type QMPs, total QMPs, or both in the replication (see Tables XXX & XXX).

It could be that original articles have to provide a clear definition as well as details on the scale, in order for a replication to be able to justify selecting the measure. A replication may also be in general more dependent on the original article for information on the definition of the constructs and the choice of measurement, compared to a description of the Operationalisation, quantification, and any modifications. These former are features of a measurement, which while preferably similar in a replication to the original, can and should be reported in the replication protocol even if the original article does not contain the details on these features itself. However, these are just speculations as the results showed no clear relations between different QMP types across original and replication (see Figure XXX), and testing of causal links was not possible with this data.

For both hypothesis 5 & 6, the results were in line with expectations, but only for the revised coding protocol. Neither hypothesis was supported by the data on QMPs obtained with the initial coding protocol. The initial protocol was revised because the ratings based on that protocol were consider to stringent, and as a result, several items were reformulated so that criteria for what constituted sufficiently clear reporting were lowered. This meant that in the revised protocol, coded QMPs would need to clearly inhibit evaluation of the measurement, whereas for the initial protocol some aspects of the measurement reporting which were coded as questionable, may have been questionable only to a small degree. As a consequence, QMPs coded with the revised protocol represent measurement practices that represent on average more questionable practices than QMPs coded with the initial protocol. With this in mind, the difference between total QMP ratio of initial and revised protocol can be seen as a form of effect size difference. It could be that only replication QMPs that represented robust violations of good measurement practices significantly lower the probability of successful replication. In that case, a stronger relation between replicability and QMPs would be found with the revised protocol, since these QMPs represented more clearly questionable practices in measurement reporting than QMPs coded with the initial protocol, which would explain the disparate results that were found.

@@

The design of this thesis came with certain limitations. First of all, there was no experimental manipulation included. As a result, the ability to investigate the exact causal links between QMPs and replicability was limited. This thesis was intended to be exploratory in nature, and thus did not focus on causal analyses. However, future research establishing causal links will prove to be very beneficial in improving the understanding of the relationships between measurement issues and replicability.

Another limitation of this study is that the results differed based on whether data from the revised or the initial coding protocol was used. As a result, any relationship between QMPs and replicability remains uncertain. The revised coding protocol was adapted from the initial coding protocol before any analyses were performed, it is however still possible that a change in protocol may have biased results. Future research investigating this topic should use a coding protocol which is verified independently by several researchers on a sample of articles and protocols first, before being used to code the QMP data that will be analysed. As a first step, the coding protocol from this thesis and the coding key from @flake2022construct can be used as a basis.

It is important to also consider whether or not replication protocols and research articles can be fairly compared in terms of QMPs. Articles are generally longer than a study's description within a replication protocol, and as a result it seems reasonable to expect research articles to generally contain more measurement details than replication protocols. Regardless, this thesis assumed that a replication protocol is comparable to an article in providing an overview of the measure and how it was used, as it is the only comparable source for such information that would otherwise be difficult to find anywhere else. This assumption seems practical if not tenable when the replication protocol is the only available sources of measurement details. However, in case more detailed information on a measurement is available in other sources, such as an online appendix, it could be important data to include when assessing QMPs. This research did not make use of any online appendices in assessing QMPs, future research may wish to include them and other sources as part of the data.

As a last note on QMPs, it is worth highlighting the way the QMP ratios were calculated. The total QMP ratio was based on the counts for each of the items from all the different QMP types divided by the total number of applicable questions. However, for each QMP type the number of items was different. This means that QMP types with a larger number of items (such as operationalisation) had a greater impact on the total QMP ratio than QMP types with a smaller number of items (such as definition). If the impact for each QMP type on each other and replicability is considered equally important, the total QMP ratio may not be considered a valid indice. On the other hand, it could be that each item should be considered equally important rather than each QMP type. For this study, the protocol was made and the analyses were conducted under the assumption that each item had equal weight. However, this is an assumption this article cannot provide evidence for.

The small sample of measures for which reliability coefficients and unidimensional factor structure could be assessed limited the degree to which substantial interpretations can be made from the reliability and validity analyses. While future research will also unlikely be able to increase the number of multiple item measures used by replications, future research can broaden their analyses to include a larger number of replications, or take into account a type of measure which this thesis mostly ignored in the analyses of reliability and validity: single-item measures.

Reliability assessment for single item measures differs substantially from multiple item measures [@wanous1996estimating], and for this reason was not included as part of the analyses for this thesis. Furthermore, single items cannot be tested on unidimensionality, since a single item is already assumed to measure only a single dimension by definition. However, future research might consider methods specifically designed to assess reliability and validity of single item measures. This could prove to be a worthwhile contribution, given the proportionally large number of single item measures that were encountered in the data for this thesis (see Figure XXX).

Finally, this paper investigated the consistency of measures, by assessing the variance in reliability across different labs wherein the measure was conducted, and comparing it to the variance in reliability between the different measures. Besides comparing the degree of reliability across labs, it is also possible to assess whether a measure assesses the same underlying construct across lab locations. This can be done through measurement invariance testing. Measurement invariance is a concept in latent factor modelling that illustrates the extent to which the relationship between items and factors is dependent on some other variable, usually a group [@mellenbergh1989item]. @shaw2020measurement investigated measurement invariance for the responses to measures at each lab location within the replication sets of Many Labs 2. Investigations similar to this have also been suggested for future replication projects [@flake2022construct]. For these reasons, future research should consider measurement invariance tests, if assessing measurement consistency in replications across different labs.

@@

Taking all the findings together, the following assessments will be relevant to consider for future replication research. With respect to the quality of measurement reporting, the small number of reported reliabilities, small number of reported psychometric validity evidence, and lack of unidimensionality evidence for data aggregated to a single indicator corroborate findings by @shaw2020measurement & @flake2022construct. Evidence supporting the measures used in replication should be reported more frequently, so that they can be evaluated and the validity of replication research can be improved.

There are additional validity issues in measurement as the result of QMPs. While it is debatable whether or not $17.9\%$ average QMP ratio in replications is too much, the association between original paper and replication protocol QMPs demonstrates how a lack of information for measurement in the original can spill over to the reporting in replications. This could lead to issues for replication attempts if the measure in an original article has poor reliability and validity. In that case, the tests in the original article are based on data from measures that do not accurately capture the construct they were intended to measure. The results of any direct replication attempt will face the same issues, and as a consequence the replication is unlikely to provide a relevant test of a psychological theory, as the original study itself was not a robust test of that psychological theory to begin with [@isager2020deciding, @isager2021deciding, @nuijten2022assessin]. Thus, future replicators should first evaluate the quality of the measurement (reporting) in an article before deciding to replicate it.

In case the quality appears low, replication attempts can still proceed with some adjustments. One option is to change the focus of the replication to be conceptual rather than direct. In that case the measure and the operationalisation can be freely altered from the original, which means that a more sufficient test of the theory can be developed. If deemed necessary, a direct replication can always be performed later based on the conceptual replication. In that case, the direct replication will be able to provide a sufficient test of a psychological theory, on the condition that the conceptual replication's test improvements led to it becoming a sufficient test.

The results also suggest that the use of structured protocols in the reporting of measurement may be an effective way of reducing QMPs, and increasing the reporting of reliability and validity evidence. However, even in the Many Labs projects, which made use of structured protocols to report their measures, low reliability and validity evidence reporting was found. These protocols could therefore still increase the attention they give to reporting reliability and validity evidence. In particular, Figure XXX shows descriptive evidence that replication protocols are lacking in definition and selection evidence. Furthermore, since replications must base their measures on those of the original articles they are replicating, it is important that articles chosen for replications provide clear evidence on what is being measured, how it is scored, why it was chosen or why it was constructed the way it is, and how it is used in practice. It is these last two aspects that original articles appear to particularly be underreporting (See Figure XXX). When original articles do not report their measurement details, replication attempts cannot guarantee a direct replication of the original. By improving the quality of measurement reporting in original articles, the validity of both original research results and future replication attempts would increase. It would be particularly important to focus on remedying strong violations of good measurement reporting, as these were shown to have a significant detrimental impact on replicability. This suggests that even small but critical improvements in the reporting of measurement information could lead to a substantial increase in the replicability of psychological science.

@@

Overall, the observed quality of measurement and frequency of measurement reporting in psychological research and replications was low, which is in line with other research on the topic. Improvements in the reporting on measurement are needed for both original and replication research. The measure source, content, and how it was used should be described in detail, and evidence illustrating the reliability and validity of the measure should be provided. Not only would the clarity of research improve, higher quality of measurement reporting in replications was shown to be related to an increase in replicability of the findings related to that measure. Tentative evidence was also found for spill-over effects of the quality of measurement reporting from original study to replications. These results combined suggest that improvements in the reporting of measurements are necessary in both replications and original articles. Furthermore, future replicators should carefully consider the quality of measurement in a study before attempting a direct replication, even considering a conceptual replication instead if the measurement in the original was not of sufficient quality. However, the evidence for the relationship between measurement quality and replicability was not robustly identified, and future research will be needed to confirm the exact nature of this relationship.
